---
name: Kiki
surname: Shimomae
position: "Marketing Specialist"
phone: +1 (949) 520-0731
www: kshimomae.github.io/website-quarto-pub/ 
email: kikishimomae7@gmail.com
linkedin: linkedin.com/in/kikishimomae/
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Globally minded digital marketing professional with a passion for blending data-driven insights with creative strategy to drive impactful outcomes. Aspires to serve as a bridge connecting people across cultures through thoughtful, engaging campaigns. Skilled in leveraging analytics to inform decision-making and enhance brand performance, with a strong interest in using digital tools to improve customer experiences and business execution. 

# Technical Skills

-   **Programming Languages:** R 
-   **Web Technologies:** HTML, CSS/SCSS, Quarto, CMS Platforms, Analytics Tools
-   **Editing:** Canva, Adobe Premiere Pro, iMovie
-   **Fluent in English and Japanese**

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ GPA,
  "Master of Science in Digital Marketing", "2023 – Expected Graduation August 2025", "California State Polytechnic University, Pomona", "4.0/4.0",
  "Bachelor of Arts in Communication", "2020 - 2022", "University of California, San Diego", "3.9/4.0"
) %>%
  detailed_entries(Degree, Year, Institution, GPA)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "July 2022 – July 2023", "Taiyo America, Inc.",
  list(
    "Operated 2 websites, created landing page designs, and wrote SEO-friendly blogs", 
    "Coordinated advertising across multiple platforms such as LinkedIn, Email, YouTube, and Magazine", 
    "Supervised trade show exhibitions, including handling booth design, advertisements, and logistics", 
    "Designed public relations strategies and handled all the processes of press releases", 
    "Created and edited graphic designs, videos, and the company’s promotional items", 
    "Processed sales orders and handled customer inquiries through phone calls, email, and social media", 
    "Performed English and Japanese translations for technical written documents and in-person/online meetings"
  ),
  "Sales and Marketing Coordinator",

  "February 2022 – June 2022", "Pinear",
  list(
    "Conducted industry and market research and analyzed data from social media platforms for improvement", 
    "Operated consistent and strategic social media posts on Instagram and LinkedIn", 
    "Edited recorded audio into 1-hour Podcast by using Adobe Premiere Pro and published bi-weekly on Spotify"
  ),
  "Social Media Manager"

) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```
